Towards Explainability of Machine Learning Models in Insurance Pricing

### 2019-10-28 manuscript/manuscript.Rmd

```{r variables, results='asis', echo = FALSE}
library(magrittr)
variables <- tibble::tribble(
  ~ Variable, ~ Type, ~ Transformation,
  "Age range", "Categorical", "One-hot encode",
  "Sex", "Categorical", "One-hot encode",
  "Vehicle category", "Categorical", "One-hot encode",
  "Make", "Categorical", "Embed in $\\mathbb{R}^2$",
  "Vehicle age", "Numeric", "Center and scale",
  "Region", "Categorical", "Embed in $\\mathbb{R}^2$"
)
knitr::kable(
  variables,
  caption = 'Input variables and their transformations.',
  booktabs = TRUE, 
  table.env='table',
  escape = FALSE,
  linesep = ""
) %>% 
  kableExtra::kable_styling(latex_options = "hold_position")
```

>>>>

```{r variables, results='asis', echo = FALSE}
library(magrittr)
variables <- tibble::tribble(
  ~Variable, ~Type, ~Transformation,
  "Age range", "Categorical", "One-hot encode",
  "Sex", "Categorical", "One-hot encode",
  "Vehicle category", "Categorical", "One-hot encode",
  "Make", "Categorical", "Embed in $\\mathbb{R}^2$",
  "Vehicle age", "Numeric", "Center and scale",
  "Region", "Categorical", "Embed in $\\mathbb{R}^2$"
)
knitr::kable(
  variables,
  caption = "Input variables and their transformations.",
  booktabs = TRUE,
  table.env = "table",
  escape = FALSE,
  linesep = ""
) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```
